hormones

### 2019-12-30 analysis/07_hormones.Rmd
new hormone analysis

>>>>

## for rechelle

```{r forrechelle}

rechelle <- hormones %>%
  dplyr::filter(hormone %in% c("prolactin", "cort"),
                treatment %in% c("lay", "inc.d9", "hatch", "n9")) %>%
  dplyr::select(-icons, -music, -iconpath, -okay)

ggplot(rechelle, aes(x = treatment, y = plasma_conc, fill = sex)) +
    geom_boxplot() + 
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
         legend.position = "none",
          strip.text = element_blank()) +
  facet_wrap(~hormone, scales = "free_y") +
  theme_B3()

write.csv(rechelle, "../results/07_forrechelle.csv")
```
